Precision calculations of the cosmic shear power spectrum projection

### 2017-02-16 limber2.tex
Made the abstract more concise

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations are negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}. For future
large-scale surveys with unprecedented precision, we show that the spherical
second-order Limber approximation will provide sufficient accuracy. \mk{The
cosmic-shear power spectrum} is in agreement with the full projection at the
sub-percent level for $\ell > 3$, and the corresponding errors an order of
magnitude below cosmic variance for all $\ell$. \mk{The shear two-point
correlation function is accurate well below one percent up to a few hundred arc
minutes. Using the fast Hankel transformation, formally defined only in flat
coordinates, to compute the two-point function from the power spectrum results
in errors below two percent compared to the spherical Legendre transformation.}
%
In the spirit of reproducible research, our numerical implementation of all
approximations and the full projection are publicly available within the
package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

>>>>

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, and first- and
second-order Limber equations for the projection. We find that the impact of
adopting these approximations are negligible when constraining cosmological
parameters from current weak lensing surveys.
%
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey
(CFHTLenS). We find that the reported tension with Planck Cosmic Microwave
Background (CMB) temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}.

For future
large-scale surveys with unprecedented precision, we show that the spherical
second-order Limber approximation will provide sufficient accuracy. \ch{In this case, the
cosmic-shear power spectrum is shown to be in agreement with the full projection at the
sub-percent level for $\ell > 3$, with the corresponding errors an order of
magnitude below cosmic variance for all $\ell$.
%We show that the commonly used 
%shear two-point correlation function is accurate well below one percent up to a few hundred arc
%minutes when adopting. 
%We find that when using the fast Hankel transformation, formally defined only in flat
%%coordinates, to compute the commonly-used two-point function from the power spectrum results
%in errors below two percent compared to the spherical Legendre transformation.}
When computing the two-point shear correlation function, we show that the flat-sky fast Hankel 
transformation results in errors below two percent compared to the full spherical Legendre transformation.}
%
In the spirit of reproducible research, our numerical implementation of all
approximations and the full projection are publicly available within the
package \textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.
